Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-09-15 WSSSPE3/report/WSSSPE3_review.tex
moving long discussions of groups from appendices to new section 6, and changing my affiliation

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(3)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ \hspace{-1.5ex}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%

@@

This report is based on collaborative notes taken during the workshop, which
were linked from the GitHub issues that represented the potential and actual
working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}), the keynote (\S\ref{sec:keynote}), and the lightning talks
presented at the meeting (\S\ref{sec:lightning}). The report also gives summaries of
action plans proposed by the working groups (\S\ref{sec:WGs}), and provides some
conclusions (\S\ref{sec:conclusions}). The first three appendices contain lists of the organizing committee
(Appendix~\ref{sec:orgcom}), the registered attendees
(Appendix~\ref{sec:attendees}), and the travel award recipients
(Appendix~\ref{sec:awardees}). Finally, the report includes longer
descriptions of the activities that occurred in each of the working groups that
made substantial progress
(Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Working Groups} \label{sec:WGs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

After this, the attendees broke up into small working groups to discuss
the remaining topics during most of the remaining 1 1/2 days.  A high-level summary
of each topic and group's work can be found in the subsections of this section, and for
all but one group, 
more detailed notes on each group's discussions can be found in Appendices~\ref{sec:appendix_best_practices}--\ref{sec:appendix_user_community}.

@@

@@

>>>>

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(3)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ \hspace{-1.5ex}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%

@@

This report is based on collaborative notes taken during the workshop, which
were linked from the GitHub issues that represented the potential and actual
working
groups\footnote{\url{https://github.com/issues?q=label\%3A\%22WSSSPE3+activity\%22}}.
Overall, the report discusses the organization work done before the workshop
(\S\ref{sec:preworkshop}), the keynote (\S\ref{sec:keynote}), and the lightning talks
presented at the meeting (\S\ref{sec:lightning}). The report also gives summaries of
action plans proposed by the working groups (\S\ref{sec:WGs}), 
then gives longer
descriptions of the activities that occurred in each of the working groups that
made substantial progress
(\S\ref{sec:group_details}), and provides some
conclusions (\S\ref{sec:conclusions}). The appendices contain lists of the organizing committee
(Appendix~\ref{sec:orgcom}), the registered attendees
(Appendix~\ref{sec:attendees}), and the travel award recipients
(Appendix~\ref{sec:awardees}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Working Groups: Summaries} \label{sec:WGs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

After this, the attendees broke up into small working groups to discuss
the remaining topics during most of the remaining 1 1/2 days.  A high-level summary
of each topic and group's work can be found in the subsections of this section, and for
all but one group, 
more detailed notes on each group's discussions can be found in \S\ref{sec:group_details}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Working Groups: Details} \label{sec:group_details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage

### 2016-09-15 WSSSPE3/report/wg_appendix_best_practices.tex
moving long discussions of groups from appendices to new section 6, and changing my affiliation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best Practices Group Discussion}
\label{sec:appendix_best_practices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Group Members}

@@

\subsection{Summary of Discussion}

@@

\subsection{Description of Opportunity, Challenges, and Obstacles}

@@

\subsection{Key Next Steps}

@@

\subsection{Plan for Future Organization}

@@

\subsection{What Else is Needed?}

@@

\subsection{Key Milestones and Responsible Parties}
\begin{itemize}
\item 28 Dec: Introduction and scope finished (Abani Patra/Sandra Gesing)
\item 06 Jan: Sections assigned (Abani Patra/Sandra Gesing)
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First version of each section
\item 15 Feb: Distribution to the WSSSPE community
\item 31 Mar: Final version of the white paper
\item 30 Apr: Submission to a peer-reviewed journal?
\end{itemize}

\subsection{Description of Funding Needed}
We might need funding for a journal publication (open-access options).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Best Practices Group Discussion}
\label{sec:appendix_best_practices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Group Members}

@@

\subsubsection{Summary of Discussion}

@@

\subsubsection{Description of Opportunity, Challenges, and Obstacles}

@@

\subsubsection{Key Next Steps}

@@

\subsubsection{Plan for Future Organization}

@@

\subsubsection{What Else is Needed?}

@@

\subsubsection{Key Milestones and Responsible Parties}
\begin{itemize}
\item 28 Dec: Introduction and scope finished (Abani Patra/Sandra Gesing)
\item 06 Jan: Sections assigned (Abani Patra/Sandra Gesing)
\item 31 Jan: Analyzing funding possibilities for survey
\item 31 Jan: First version of each section
\item 15 Feb: Distribution to the WSSSPE community
\item 31 Mar: Final version of the white paper
\item 30 Apr: Submission to a peer-reviewed journal?
\end{itemize}

\subsubsection{Description of Funding Needed}
We might need funding for a journal publication (open-access options).

### 2016-09-15 WSSSPE3/report/wg_appendix_industry_interaction.tex
moving long discussions of groups from appendices to new section 6, and changing my affiliation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transition Pathways to Sustainable Software: Industry \& Academic Collaboration Working Group Discussion}
\label{sec:appendix_industry_interaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{What Else is Needed?}
Nothing at the moment.

\subsection{Key Milestones and Responsible Parties}

@@

\subsection{Description of Funding Needed}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Transition Pathways to Sustainable Software: Industry \& Academic Collaboration Working Group Discussion}
\label{sec:appendix_industry_interaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{What Else is Needed?}
Nothing at the moment.

\subsubsection{Key Milestones and Responsible Parties}

@@

\subsubsection{Description of Funding Needed}
